---
title: "VALUATION OF CULTURAL ECOSYSTEM SERVICES IN URBAN PARKS"
authors: "Carlos, Claudiano e ... "
output: 
  pdf_document:
     latex_engine: xelatex
bibliography: bibliography.bib
biblio-style: spphys
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction {#intro}

The world population may grow 26% by the year 2050, from the current 7.7 billion to 9.7 billion[@un2019]. This will lead to an even greater increase in the population in urban areas, especially in regions such as Latin America that already have around 81% of their population living in these areas [@un2018]. This scenario increases the concern with maintaining and / or improving the well-being conditions for this population. And in this regard, it is considered that the well-being of the inhabitants of urban areas depends on an adequate supply of ecosystem services [@keeler2019social].

Understood as nature's contributions to people, ecosystem services are vital for human existence and good quality of life. However, they are generally distributed unevenly in space, time and between different segments of society [@diaz2019global]. Of particular interest to the well-being of urban populations, cultural ecosystem services are public goods, produced by ecosystems that affect people's physical and mental states. Cultural services are characterized mainly as environments, places or environmental situations that give rise to changes in people's physical or mental states [@haines2018revision]. And therefore, in a context of greater urbanization, special attention should be paid to urban green spaces as a guarantee of offering this type of ecosystem service, and ensuring the integration of these spaces in city planning [@liu2020supply].

These benefits provided by urban green areas are still important when cities seek to offer a variety of services that contribute to increasing the quality of life of their inhabitants. Initiative that already found support in the agenda of the Sustainable Development Goals - SDGs, gains even more momentum with the greater importance given to these spaces after the long period of confinement caused by the Pandemic of COVID-19.

However, unlike developed countries, in Brazil and Latin America, the literature on this issue is still scarce. There are few studies that explore the association between green areas and well-being in urban areas in Brazil [@amato2016metropoles; @camargo2018physical; @londe2014influencia; @silveira2018espaccos]. There are also few studies on the economic valuation of these areas. These productions are concentrated in the southern region of the country and focused on individual parks. And in general, cultural ecosystem services are less evaluated or evaluated inappropriately [@ridding2018importance] and for this reason they are seldom present in studies in this area [@boerema2017ecosystem]. This scarcity makes it difficult to understand the potential benefit that urban green spaces can bring to the Brazilian population [@arana2017qualidade]. And the importance of investments by the government in these areas.

In this article, we seek to contribute to fill this information gap and demonstrate the importance of urban parks as sources of provision of cultural ecosystem services in the city of Recife. As a differential, we do not study only one park, but all urban parks recognized by the city and which had specific equipment for physical activities. We used questionnaires applied to users of all parks to characterize them and we used the contingent valuation method to estimate the monetary value. Among other contributions, the results demonstrate that the parks in Recife have a greater coverage than usual and that users with lower income groups value these areas more than users with lower income.


# Methodology {#sec:1}

## Study Area  {#sec:2}

The place of study was the Municipality of Recife, capital of the state of Pernambuco, in the Northeast region of Brazil. The municipality has 10 public parks and countless squares spread over the 94 neighborhoods that compose it. The area covered by the squares parks is equivalent to 8.2% of the municipal territory. These 10 areas have structures known as city gyms, spaces with equipment and classes of different modalities, in addition to other leisure equipment (Figure 1).

**inserir figura do mapa**

## Survey methods and questionnaire design

We conducted the survey between December 2018 and March 2019 among the local residents of the city of Recife that uses at least one of the 9 parks of the city. The survey method was face-to-face personal interviews by means of a structured questionnaire and was applied to 1281 questionnaires. All procedures were according to the rules of resolution 510/1617 of National Health Council (CNS), the opinion survey format was prepared and did not request any identification. 

We gathered data among the Recife users population’s universe, configuring a non-probabilistic sample with a convenience bias. We recognize the sampling scheme has not achieved a representative sample of the city’s households. All the analyses and estimates were performed with the R Studio 4.0 software. The dataset is available in csv format at a Github repository [https://github.com/cccneto/valuation_urbanParks].

The current survey was tested through a pilot study/previous survey in one of the city parks [@cruzneto2021]. We have constructed the bid vector for the dichotomous choice questions based on the analysis of the WTP respo   nses in the previous survey. The questionnaire’s structure was based on the NOAA panel recommendations for CVM studies [@arrow1993report]. The questionnaire consisted of a set of 17 questions. 

In the first part, we surveyed respondents’ socio-economic and household characteristics from age at least 18 years. In the second part we asked about: a) the visit purpose to the park, b) the frequency visits to the park, c) the main criteria determining the decision to visit a park,  d) their perceptions about the park characteristics (e.g. Facilities, maintenance, size, security), finally, e) their perception about the presence of ecosystem services in the park.

The final part we described the hypothetical scenario and the valuation questions. In this scenario, we presented a change in the park's vegetal cover to the respondents, focusing on the transformation of the environmental quality of the area. It is important to say the interviewer did a relevant visual presentation of the changes in the scenario presented (i.e. images before and after the park development).

In the approach to respondents on the park, we asked residents if they wanted to participate in this research (i.e., if they agree to respond to the survey questions). After the two initial parts of the questionnaire, we asked how much they would be willing to pay for the changes presented to them. The interviewer explained their answers would be useful to the decision-making and planning process. About the WTP question, we adopted a close-ended format to better approximate real market transactions (i.e., take-it or leave-it decisions).  We have have adopted the a double-bounded (DB) dichotomous choice format following the recommendations of the NOAA panel [@arrow1993report] and [@hanemann1991statistical]. The procedures presents to respondents an initial bid value, randomly selected from a set of 70 bid levels - R\$ 1 to R\$ 70. If the response was “yes” a follow-up question with a higher bid was asked, while a “no” response led to a lower bid level. The value amount would be annually collected by the municipal authority and would be exclusively devoted to cover the development costs of the park. 

## Theoretical Model 

According to [@groothuis2002does], econometric models of dichotomous choice have been an instrument widely used to address issues related to contingent valuation. O Modelo de utilidade randômica fornece as bases teóricas para a análise de Métodos de Valoração Contingente.In this model an individual could choose to pay a donation fee for the conservation of the services provided by the studied area if the following conditions are met (Hanemann, 1984):

\begin{align}
u(y, X) = u(y-t, q, X)
\end{align}

\begin{align}
u(y, X) = u(y_{j}X_{j}) + \epsilon_{0j})
\end{align}

\begin{align}
v(1, y-t; X) + \epsilon_{1} \ge v(0, y, X)
\end{align}

Where $u$ is the respondent's utility function, $v$ is the indirect utility function, $1$ represents the donation payment and $0$ represents the non-payment, $y$ is the respondent's individual income, the amount of the bid made to the respondent, $X$ represents other socioeconomic characteristics that affect the respondent's preferences. The difference between the utilities $\Delta v$ determines the payment or not of the donation:

\begin{align}
\Delta v= (1, y-t;X) -v(0, y, X) + \epsilon_{1} + \epsilon_{0} 	
\end{align}

The MVC dichotomous choice format requires a qualitative choice model. The use of a linear distribution of the WTP and a Bivariate Probit Model (BPM), was developed based on the model by [@cameron1994estimation]. It is assumed that the error of the second dichotomous question is correlated with the error of the first question. For this reason, we follow Alberini's (1995) recommendation for the choice of bivariate dichotomous models, because if the coefficient correlation, $\rho \ne 1$, it is clear that, in general, the second WTP does not perfectly match the first and can be interpreted as a revised version of the amount of the first WTP. If WTP values are independently determined, then $\rho = 0$. For all other values of the correlation coefficient, the interval $0 < \rho < 1$ is valid, which implies that the correlation between the two WTP values is less than perfect.

Considering these aspects, the modeling of the data generated by the questions in the double limit dichotomous choice format was achieved by the following formulation:

#### Linear Model 

$$
\begin{aligned}
\Delta Y_{i}(yes|no)= \alpha_{0} + \alpha_{1}Age + \alpha_{2}D_{1i} + \alpha_{3}D_{2i} \\ 
+ \alpha_{4}D_{3i} + \alpha_{5}D_{4i} + \alpha_{6}Tempo_{i} + \beta_{1}Bid_{12i} + \epsilon_{i} 	
\end{aligned}
$$

$Y_i$ is the dependent variable and reports the respondent's answer ($yes = 1$ or $no = 0$) to the $Bid$, $Age_i$ is the age of the respondent, $D_{1i}$ is the dummie variable for the $Sex$ of the respondent (man = $1$, woman = $0$), $D_{2i}$ is a dummie for the respondent's education (complete higher education = $1$), $D_{3i}$ is a dummie for respondent assessing regarding the temperature in the park (good / excellent = $1$), $D_{4i}$ is a dummie for assessing the respondent regarding of the park's Facilities (good / great = $1$), $Bid_i$ are the variables for the values drawn as bids to respondents.

The $WTP_{ij}$ component represents the respondent's $j-th$ willingness to pay and $i = 1$, 2 denotes the first and second questions, respectively.

\begin{align}
WTP_{ij} = X'_{ij}\beta_{i} + \epsilon_{ij}
\end{align}

The $WTP$ depends on a systematic component given by the observed characteristics of the interviewee $(X'_{ij}\beta_{i})$, as well as a random random component $(ij \sim N(0, \sigma^2))$.     

\begin{align}
Pr(yes, no) = Pr(WTP_{1j} \ge t^1, WTP_{2j} < t^2)
\end{align}

\begin{align}
Pr(yes, no) = Pr(X'_{1}\beta_{1} + \epsilon_{1j} \ge t^1, X'_{2}\beta_{2} + \epsilon_{2j} < t^2)
\end{align}

Since the other sequence of possible responses can be constructed in an analogous way, which allows building the likelihood function:

$$
\begin{aligned}
L_{j} (\mu | t) = Pr(X'_{1}\beta_{1} + \epsilon_{1j} \ge t^1, X'_{2}\beta_{2} + \epsilon_{2j} < t^2)^{yn} * \\
Pr(X'_{1}\beta_{1} + \epsilon_{1j} < t^2 , X'_{2}\beta_{2} + \epsilon_{2j} \ge t^2)^{ny} * \\
Pr(X'_{1}\beta_{1} + \epsilon_{1j} > t^1, X'_{2}\beta_{2} + \epsilon_{2j} \ge t^2)^{yy} * \\ 
Pr(X'_{1}\beta_{1} + \epsilon_{1j} < t^1, X'_{2}\beta_{2} + \epsilon_{2j} < t^2)^{nn} 
\end{aligned}
$$

Given a sample of n respondents, we have that the function of logarithmic probability of the responses to the first and second moves of the dichotomous choice with double limit is:

$$
\begin{aligned}
Ln(L_{j} (\mu | t)) = yn \ln((X'_{1}\beta_{1} + \epsilon_{1j} \ge t^1, X'_{2}\beta_{2} + \epsilon_{2j} < t^2) * \\
ny Pr(X'_{1}\beta_{1} + \epsilon_{1j} < t^2 , X'_{2}\beta_{2} + \epsilon_{2j} \ge t^2) * \\
yy Pr(X'_{1}\beta_{1} + \epsilon_{1j} > t^1, X'_{2}\beta_{2} + \epsilon_{2j} \ge t^2) * \\
nn Pr(X'_{1}\beta_{1} + \epsilon_{1j} < t^1, X'_{2}\beta_{2} + \epsilon_{2j} < t^2)) 
\end{aligned}
$$

Once the regression is estimated, the estimated WTP is calculated as:

\begin{align}
\widehat{WTP} = \frac{\hat{\alpha}\overline{X_{i}}}{\hat{\beta}} 
\end{align}


# Results {#sec:3}

## Respondent's profile

After processing the data, 1144 questionnaires were used. Considering the estimated population of 1,653,461 inhabitants of the city, and the distribution between age groups, income, sex and place of residence, the data are representative for the city. Among the interviewees, $51.68\%$ were female; $48.32\%$ male. The vast majority of respondents $92.82\%$ were young adults (<65 years), living in 94 neighborhoods in the city (Table 1).

```{r include=FALSE}
library(tidyverse)
library(readxl)
library(DCchoice)
library(Ecdat)
library(lmtest)
library(dplyr)
library(VIM)
library(GJRM)
library(tidyr)
library(utils)
library(kableExtra)

# base <- utils::read.table("https://raw.githubusercontent.com/cccneto/valuation_urbanParks/master/dados/base_cleaned.csv",
#                   header = T,
#                   sep = ",")
# 
# base <- read.csv("https://raw.githubusercontent.com/cccneto/valuation_urbanParks/master/dados/base_cleaned.csv", 
#                  header = T)


# Carregando base de dados
url <- "https://github.com/cccneto/valuation_urbanParks/blob/master/dados/baseunificada.xlsx?raw=true"
destfile <- tempfile()
curl::curl_download(url, destfile)
baseunificada <- read_excel(destfile)


baseunificada <- baseunificada %>% 
  select(parque, idade, sexo, cidade, escolar, renda, infraestrutura, sombra, temperatura, objetivo, 
         lance1,lance2, resp1, resp2, bidl, bidh, lnRendat1, lnRendat2, lnRenda) %>% 
  mutate(
    infraestrutura = as.double(infraestrutura),
    sombra = as.double(sombra),
    temperatura = as.double(temperatura))

# Ajustando codigo de variaveis

base <- baseunificada %>%
  mutate(
    infraestrutura = case_when(infraestrutura >= 4 ~ "1", TRUE ~ "0"), 
    temperatura = case_when(temperatura >= 4 ~ "1", TRUE ~ "0"),
    sombra = case_when(sombra >= 4 ~ "1", TRUE ~ "0"),
    escolar = case_when(escolar > 19 ~ "1", TRUE ~ "0"), # 1=superior completo, 0= otherwise
    sexo = case_when(sexo == 1 ~ "1", TRUE ~ "0")
  )

base <- base %>%
  mutate(
    parque = as.factor(parque),
    idade = as.integer(idade),
    sexo = as.integer(sexo),
    cidade = as.factor(cidade),
    escolar = as.integer(escolar),
    renda = as.integer(renda),
    infraestrutura = as.integer(infraestrutura),
    sombra = as.integer(sombra),
    temperatura = as.integer(temperatura),
    lance1 = as.integer(lance1),
    lance2 = as.integer(lance2),
    resp1 = as.factor(resp1),
    resp2 = as.factor(resp2)
  )




base %>%
  select(
  resp1, resp2, lance1, lance2, idade, sexo, escolar, infraestrutura, temperatura, renda, parque, objetivo) %>%
  summarytools::dfSummary(graph.col = F, valid.col = F, na.col = F) %>% 
  print()

```

Inserir tabela considerando a informação **Objetivo de visita** 

```{r eval=FALSE, include=FALSE}
# ANALISE CONJUNTA DE TODOS OS PARQUES

## Configurando listas de variaveis - **modelo sem renda**
treat.eq <- resp1 ~ lance1 + idade + sexo + escolar + temperatura + infraestrutura
out.eq <- resp2 ~ lance2 + idade + sexo + escolar + temperatura + infraestrutura
f.list <- list(treat.eq, out.eq)
mr <- c("probit", "probit")

## Modelo Linear
bvp <- gjrm(f.list, data=base, Model="B", margins= mr)
summary(bvp)

library(modelsummary)
modelsummary(bvp, group = component + term ~ model)

coefs <- summary(bvp)
coefs$tableP1
coefs <- summary(bvp$coefficients)

# atribuindo valores médios
lance1_med <- mean(base$lance1)
renda_med <- mean(base$renda)
idade_med <- mean(base$idade)
sexo_med <- mean(base$sexo)
escolar_med <- mean(base$escolar)
temp_med <- mean(base$temperatura)
infra_med <- mean(base$infraestrutura)
lance2_med <- mean(base$lance2)

## coeficientes eq 1
cf_intercept1 <- bvp$coefficients[1]
cf_lance1 <- bvp$coefficients[2]
cf_idade <- bvp$coefficients[3]
cf_sexo <- bvp$coefficients[4]
cf_escolar <- bvp$coefficients[5]
cf_temp <- bvp$coefficients[6]
cf_infra <- bvp$coefficients[7]

# coeficientes eq 2
cf_intercept2 <- bvp$coefficients[8]
cf_lance2 <- bvp$coefficients[9]
cf_idade2 <- bvp$coefficients[10]
cf_sexo2 <- bvp$coefficients[11]
cf_escolar2 <- bvp$coefficients[12]
cf_temp2 <- bvp$coefficients[13]
cf_infra2 <- bvp$coefficients[14]

## CALCULANDO A DAP 

### Dap equação 1
dap_eq1 <- -( cf_intercept1 + cf_idade*idade_med + cf_sexo*sexo_med + cf_escolar*escolar_med + cf_temp*temp_med + cf_infra*infra_med)/cf_lance1 # R$ 40,47

# A dap da equação 1 foi de R$ 
round(dap_eq1, digits = 2)

### Dap equação 2
dap_eq2 <- -(cf_intercept2 + cf_idade2*idade_med + cf_sexo2*sexo_med + cf_escolar2*escolar_med + cf_temp2*temp_med + cf_infra2*infra_med)/cf_lance2 # R$ 32,69 

# A dap da equação 2 foi de R$ 
round(dap_eq2, digits = 2)
round(dap_eq1, digits = 2)
# Análise individual dos parques

wtp1_median <- as.numeric(median(base$lance1))
wtp1_mean <- as.numeric(lance1_med)
wtp1_estimated <- as.numeric(dap_eq1) 
wtp2_median <-  as.numeric(median(base$lance2))
wtp2_mean <- as.numeric(lance2_med)
wtp2_estimated <- as.numeric(dap_eq2)

teste <- 
  rbind(wtp1_median,wtp1_mean, wtp1_estimated, wtp2_median, wtp2_mean, wtp2_estimated) %>%  
  as.data.frame() %>% 
  round(digits = 2)

df <- as_tibble(teste)

Values <- teste$V1   
WTP  <- c("wtp1_median","wtp1_mean", "wtp1_estimated", "wtp2_median", "wtp2_mean", "wtp2_estimated")

# tabela com valores de WTP
wtps <- cbind(WTP, Values) 

```



```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
base %>%
  select(
    resp1, resp2, lance1, lance2, idade, sexo, escolar, infraestrutura, temperatura, renda) %>%
  summarytools::dfSummary(graph.col = F, valid.col = F, na.col = F) %>% 
  print()
   
```

Regarding the profile of respondents, $45.9\%$ of the respondents are female, the average age is about 41.3 years (sd = 14.8). The average monthly income is $R\$ 1.800$, and the median income was estimated to be between $R\$ 41$ and $R\$ 61.200$. Only $25.9\%$ hold a degree from a university or from a technological educational institute.About the use of dummy variables, we focused on respondents assessing their self-perception on the temperature in the park, and regarding the park's Facilities. About $31.8\%$ beliefs that the park has a nice temperature because of the natural cover to the park. And $55.4\%$ evaluated the "Facilities as good/great. These variables  were included in the analysis because it was expected to affect positively the probability to participate in the project, as well the respondent's WTP.(ver tabela x)


```{r include=FALSE}
# Proporção de respostas por parque
resp_parq <- base %>% 
  group_by(parque) %>% 
  na.omit() %>% 
      mutate(resp1 = as.numeric(resp1),
             resp2 = as.numeric(resp2)) %>% 
      summarise(yy = sum(resp1==1 & resp2==1),
                yn = sum(resp1==1 & resp2==0),
                ny = sum(resp1==0 & resp2==1),
                nn = sum(resp1==0 & resp2==0)) %>% 
    group_by(parque) %>%
    summarise(freq_yy = yy / sum(yy, yn, nn, ny)*100,
            freq_yn = yn / sum(yy, yn, nn, ny)*100,
            freq_ny = ny / sum(yy, yn, nn, ny)*100,
            freq_nn = nn / sum(yy, yn, nn, ny)*100,
            total_quest = sum(yy, yn, nn, ny))  %>% 
    arrange(desc(freq_yy, freq_yn)) 

resp_parq
```

**Inserir detalhamento das respostas por parque e geral**

```{r include=FALSE}
# respostas por parque
num_total <- base %>% 
  na.omit() %>% 
  mutate(resp1 = as.numeric(resp1),
         resp2 = as.numeric(resp2)) %>% 
  summarise(yy = sum(resp1==1 & resp2==1),
            yn = sum(resp1==1 & resp2==0),
            ny = sum(resp1==0 & resp2==1),
            nn = sum(resp1==0 & resp2==0)) 

num_total
```

```{r include=FALSE}
# frequencia das respostas - todos parques
freq_total<- num_total %>%  
  summarise(freq_yy = yy / sum(yy, yn, nn, ny)*100,
            freq_yn = yn / sum(yy, yn, nn, ny)*100,
            freq_ny = ny / sum(yy, yn, nn, ny)*100,
            freq_nn = nn / sum(yy, yn, nn, ny)*100) %>% 
  arrange(desc(freq_yy, freq_yn)) %>% 
  round(digits = 2)

freq_total
```


## Bivariate Probit Model estimation results

The results from the BP regression for the general sample are shown in Table x. The estimations for Eq. (1) are shown in the upper part of the Table, while the estimation for Eq. (2)  in the lower part. The probability that WTP be equal or higher to the two bids amount is influenced by the respondent’s own characteristics and by a series of independent variables that reflect their preferences for the ES being valued. The coefficient on the bid was negative and statistically significant in both equations, which indicates as the price increased the probability of a positive answer to the WTP question decreased.  

 \begin{table}[!tbp]
    \begin{center}
    \begin{tabular}{lrrrr}
    \hline\hline
    \multicolumn{1}{l}{}&\multicolumn{1}{r}{Estimate}&\multicolumn{1}{r}{Std. Error}&\multicolumn{1}{r}{z-value}&\multicolumn{1}{r}{p-value}\tabularnewline
    \hline
       \vspace{5mm}
   \textbf{Equation 1} \\
    \textit{Intercept} & $0.635419$ & $0.1440$ & $4.410$ & $0.00001$ \tabularnewline
    Bid1 & $-0.020311$ & $0.0020$ & $-10.154$ & $0.00000$ \tabularnewline
    Age& $-0.006643$ & $0.0026$ & $-2.540$ & $0.01109$ \tabularnewline
    Gender & $0.073047$ & $0.0776$ & $0.941$ & $0.34666$ \tabularnewline
    School & $0.216602$ & $0.0915$ & $2.367$ & $0.01795$ \tabularnewline
    Temperature & $0.270258$ & $0.0863$ & $3.131$ & $0.00174$ \tabularnewline
    Facilities & $0.503613$ & $0.0808$ & $6.226$ & $0.00000$ \tabularnewline
    \hline
\vspace{5mm}
   \textbf{Equation 2} \\
     \textit{Intercept} & $ 0.528728$ & $0.1418$ & $3.728$ & $0.00019$\tabularnewline
    Bid2 & $-0.015654$ & $0.0019$ & $-7.832$ & $0.00000$\tabularnewline
    Age & $-0.010806$ & $0.0.0025$ & $-4.272$ & $0.00001$\tabularnewline
    Gender & $0.172253$ & $0.0740$ & $2.37$ & $0.019989$\tabularnewline
    School & $-0.067069$ & $0.0869$ & $-0.771$ & $0.44074$\tabularnewline
    Temperature & $-0.025151$ & $0.0832$ & $-0.302$ & $0.76265$\tabularnewline
    Facilities & $0.651171$ & $0.0770$ & $8.452$ & $0.00000$\tabularnewline
   \hline
   Nº Observations & & & &  $1144$ \tabularnewline
   Log Likelihood & & & & $-1342.32$ \tabularnewline
   AIC & & & & $2714.6$ \tabularnewline
   BIC & & & & $2790.3$ \tabularnewline
   \hline
   \end{tabular} \end{center}
       \end{table}
       
```{r include=FALSE}
# ANALISE CONJUNTA DE TODOS OS PARQUES

## Configurando listas de variaveis - **modelo sem renda**
treat.eq <- resp1 ~ lance1 + idade + sexo + escolar + temperatura + infraestrutura
out.eq <- resp2 ~ lance2 + idade + sexo + escolar + temperatura + infraestrutura
f.list <- list(treat.eq, out.eq)
mr <- c("probit", "probit")
```

```{r include=FALSE}
## Modelo Linear
bvp <- gjrm(f.list, data=base, Model="B", margins= mr)
summary(bvp)

```

The results for the general sample indicate that WTP from the first equation (Eq 1) was influenced positively by the level of education (0.2166, p-value < 0,05), and by the respondent's perceptions about Facilities (0.5036, p-value < 0,01) and temperature of the park (0.2702, p-value < 0,01), while the respondent's gender was statistically significant just in the second equation.

Our results allow us to highlight the find that the respondents' age has a statistically significant negative impact on both the respondents’ initial and follow-up decisions on their contribution to realizing the presented scenario. The regression coefficient is (-0.0066, p-value < 0,05) at the respondents’ initial response and (-0.0108, p-value < 0,01) at the follow-up response, which means that the higher the age, the lowest the probability that the respondent shall accept the proposed willingness-to-pay value. 

Examining just the second equation, the results for the general sample indicate that WTP is negatively influenced by the age of respondents (0.010, p-value < 0,01), by the park's temperature (0.090, p-value < 0,01), and the respondent's gender (0.042, p-value < 0,186). However, it is positively affected by respondent's perceptions about the park's Facilities (0.176, p-value < 0,01). Opposite to the first equation, the level of education wasn't statistically significant.

Examining the results, we could interpret some of the signs of the estimated coefficients as expected and consistent with the economic theory. For example, the likelihood of voting “yes”  to the proposed program in the second equation is higher for younger and better-educated respondents, as well as for female respondents. It's not certain, but the age results can be explained by the high average age of the respondents (41 years). On the other hand, we find that likelihood of voting “yes”  to the proposed program is lower when we consider park respondent's temperature perceptions. Furthermore, the regression model indicates statistically significant and theoretically justify relationships between the WTP responses and several explanatory variables.


# Discussion {#sec:4}


[@brander2011value] An important finding from the meta-analyses is that the methodological design of the underlying valuation study has a large influence on the results of both CV.

Ver secao 5.3. Determinants of the true willingness to pay Let us now consider the impacts of the determinants de [@verbivc2016contingent]

# Conclusions {#sec:5}

Estimating the benefits provided by green areas in urban spaces is not an easy task, especially in public projects. However, this difficulty should not be seen as an insurmountable condition. For this reason, we endeavor to obtain a monetary measure derived from the benefits extracted by the users of the parks, especially from their direct use value of the Cultural Ecosystem Services, such as the use of the parks of the City of Recife for the recreational activities of its visitors.

We find that urban parks and green spaces are quite important to the local population. For that reason, one of the exercises proposed in this article was precisely to estimate the willingness to pay of park users and measure the total surplus of that provision. We address the need to recover a green area (park), highlighting its importance as an alternative in improving the quality of life of the population benefited by the studied area. In fact, our results are restricted to the urban population of the city where parks are located (Recife - Brazil), which does not prevent our estimates from being compared with the similarities of other cities in developing countries.

In general, our findings suggest that part of the population of Recife attributes a positive economic benefit to the urban park, and for this reason, they expressed a positive Willingness to Pay. We believe that this result was possible because of the positive effect of park to his users. Our results also reveal that the value of the bids offered had a greater influence on the Respondents' Willingness to Pay. The Estimated WTP for the model was R\$ 40.47 (first bid) and R\$ 32.69 (second bid). which totaled a consumer surplus of R\$ 545,151.90 and R\$ 568,075.52.


# Policy implications and Recomendations

Like any economic methodology, contingent valuation has its limitations and it alone can never provide the definitive answer to any major policy question (Carson, 1998).

This study introduces a new approach to calibrate WTP estimates using perceived policy consequentiality that enables detailed analyses of the factors behind preference misrepresentations [@liu2020effects]. The perceived consequentiality reduces the probability of nontruthful choices and potentially leads to a more accurate willingness to pay (WTP) estimation
 
In accordance with [@liu2020effects], policy consequentiality refers to the belief of respondents that their survey responses will affect the outcome of whether a proposed policy or project is implemented. Payment consequentiality refers to the belief that payment will be imposed when the project gets implemented. Truthful preference revelation is unlikely when survey respondents do not believe that the survey is consequential [@carson2007incentive], which may bias estimation on WTP.
 
ACRESCENTAR comentário nas discussões a respeito de preferirmos imposto ou cobrança direto na conta ao inves de doação" -> \textbf{The tax payment vehicle is generally preferred to the voluntary donation payment vehicle as the tax reduces free-riding incentives when true WTP is higher than the elicited amounts.}
 
Verificar texto do [@latinopoulos2016valuing] 

# References 